Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-02-02 manuscript/supplements_rsfmri.Rmd

#library(lsr)
library(wesanderson) # colour palette
#library(haven)

@@

```{r "knit setup", include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex")
options(knitr.kable.NA = '') # hide NA in tables
# set working directory of knit (RMarkdown) to directory of Rproj
opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
setwd(knitr::opts_knit$get("root.dir"))
source('report/figures.R')
source("report/tables.R")
source("report/create_sample_df.R")
```

## Interaction effect group by time on aggregated FC (preregistered analysis)
```{r load agg FC data and prepare, echo=FALSE}
final=readRDS("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/tab/final.rds")

agg_FC_DMN=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/DMN/agg_FC_DMN.txt")
agg_FC_DMN_ID=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/DMN/agg_FC_DMN_ID.txt")
agg_FC_Rew_ID=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/Rew/agg_FC_Rew_ID.txt")
agg_FC_Rew=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/Rew/agg_FC_Rew.txt")
for (i in c(1:nrow(agg_FC_DMN_ID))){
  tmp=strsplit(base::strsplit(as.character(agg_FC_Rew_ID[i,"V1"]),'/')[[1]][10],'_nacc')[[1]][1]
  agg_FC_Rew[i,"subj.ID"]=strsplit(tmp,"_")[[1]][1]
  agg_FC_Rew[i,"tp"]=strsplit(tmp,"_")[[1]][2]
  tmp=strsplit(base::strsplit(as.character(agg_FC_DMN_ID[i,"V1"]),'/')[[1]][10],'_pcc')[[1]][1]
  agg_FC_DMN[i,"subj.ID"]=strsplit(tmp,"_")[[1]][1]
  agg_FC_DMN[i,"tp"]=strsplit(tmp,"_")[[1]][2]
}

colnames(agg_FC_Rew)=c("mean_Rew_conn","sd_Rew_conn","subj.ID", "tp")
colnames(agg_FC_DMN)=c("mean_DMN_conn","sd_DMN_conn","subj.ID","tp")

final_FC=merge(final, agg_FC_Rew, by=c("subj.ID","tp"), all.x=TRUE)
final_FC=merge(final_FC, agg_FC_DMN, by=c("subj.ID","tp"), all.x=TRUE)
final_FC$subj.ID=as.factor(final_FC$subj.ID)
final_FC$group_factor=relevel(final_FC$group_factor, ref = "KG")

#calculate mean BMI over timepoints
final_FC.meanBMI=tapply(X=final_FC$BMI,
                        INDEX=final_FC$subj.ID, FUN=mean, na.rm=TRUE)
final_FC$mean.BMI=
  final_FC.meanBMI[as.numeric(final_FC$subj.ID)]
final_FC$within.BMI=
  final_FC$BMI-final_FC$mean.BMI

#calculate mean FD over timepoints
final_FC.meanFD=tapply(X=final_FC$logmFD,
                        INDEX=final_FC$subj.ID, FUN=mean, na.rm=TRUE)
final_FC$mean.logmFD=
  final_FC.meanFD[as.numeric(final_FC$subj.ID)]
final_FC$within.logmFD=
  final_FC$logmFD-final_FC$mean.logmFD
```

@@

```{qa check DMN model age,sex, echo=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

@@

```{qa check DMN model age,sex, mFD, echo=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

@@

```{r DMN conn over three timepoints, echo=FALSE}
fig_DMNconn<-mk_figDMNdescr(final_FC)
fig_DMNconn
```

### Reward network for two time points, adjusted for age and sex (Model 1a)
```{r calc rew two tp, age, sex, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +  (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tp=anova(R1,R0)
```
```{qa check Rew model age,sex, echo=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

@@

```{qa check Rew model age,sex,mFD, echo=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

@@

### Reward network for three timepoints, adjusted for age, sex, mean FD (Model 1b)
```{r calc rew three tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + logmFD +(1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +logmFD +(1|subj.ID), data=final_FC)
anvRew3tp=anova(R1,R0)
```
```{r Rew3tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), reorder.coef=c(1, 2, 3, 4, 8,9,5,6,7),custom.coef.names=c("Intercept (BL, NBARS)", "Timepoint FU", "Timepoint FU2", "Group BARS", "Age", "Sex","logmFD","Timepoint FU x Group", "Timepoint FU2 x Group"), custom.model.names = c("R0", "R1"), float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```
```{r Rew conn over three timepoints, echo=FALSE}
fig_Rewconn<-mk_figRewdescr(final_FC)
fig_Rewconn
```

>>>>

#library(lsr)
#library(haven)
library(wesanderson) # colour palette

@@

```{r "knit setup", include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex")
options(knitr.kable.NA = ' ') # hide NA in tables
# set working directory of knit (RMarkdown) to directory of Rproj
```

```{r "tableSample", echo=FALSE}

tableSample <- readRDS(file = "../report/tab/tableSample.rds")

tab <-
  knitr::kable(
    tableSample,
    row.names = TRUE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = "Distribution of data points at months after intervention")
tab
```

```{r tableDescr, include=FALSE}
# table for descriptive statistics
tableDescr <- readRDS(file = "../report/tab/tableDescr.rds")

knitr::kable(
    tableDescr,
    row.names = FALSE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = "BMI and mean FD of participants acquired in each condition and time point")
```

```{r figDesignmatrix, fig.align = 'center', fig.ncol = 2, out.width = "50%", fig.subcap = c('Design matrix with time as categorial factor.','Design matrix with time as continuous variable.'), fig.cap="Possible design matrices of time-by-group model.", echo=FALSE}
DesignMatricesList <- readRDS(file = "../report/fig/DesignMatricesList.rds")
DesignMatricesList$plotA
DesignMatricesList$plotB
#gridExtra::grid.arrange(plotA, plotB, nrow=1)
```

```{r figtSNR,fig.cap="Lower tSNR in the region of interest NAcc versus precuneus used for seed-based connectivity (shown are all 101 timepoints)", out.width="40%", eval=FALSE}
tsnr <- "../report/tsnr.pdf"
knitr::include_graphics(tsnr)
```

## Interaction effect group by time on aggregated FC (preregistered analysis)
```{r load agg FC data and prepare, echo=FALSE}
final_FC <- read.csv("../report/final_FC.csv")
```

@@

```{r qa check DMN model age,sex, echo=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

@@

```{r qa check DMN model age,sex, mFD, echo=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

@@

```{r DMN conn over three timepoints, echo=FALSE}
fig_DMNconn <- readRDS(file = "../report/fig/figDMNconn.rds")
fig_DMNconn
```

### Reward network for two time points, adjusted for age and sex (Model 1a)
```{r calc rew two tp, age, sex, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +  (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tp=anova(R1,R0)
```
```{r qa check Rew model age,sex, echo=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

@@

```{r qa check Rew model age,sex,mFD, echo=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

@@

### Reward network for three timepoints, adjusted for age, sex, mean FD (Model 1b)
```{r calc rew three tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + logmFD +(1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +logmFD +(1|subj.ID), data=final_FC)
anvRew3tp=anova(R1,R0)
```
```{r Rew3tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), reorder.coef=c(1, 2, 3, 4, 8,9,5,6,7),custom.coef.names=c("Intercept (BL, NBARS)", "Timepoint FU", "Timepoint FU2", "Group BARS", "Age", "Sex","logmFD","Timepoint FU x Group", "Timepoint FU2 x Group"), custom.model.names = c("R0", "R1"), float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```
```{r Rew conn over three timepoints, echo=FALSE}
fig_Rewconn <- readRDS(file = "../report/fig/figRewconn.rds")
fig_Rewconn
```
